Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-21 trunk/constantRate/ConstCompFuzzExt.tex
Cleaned up revised proof of first construction

\begin{abstract} 
Fuzzy extractors derive strong keys from noisy sources.  The goal is to reliably convert a high entropy source~(which may have different values on repeated readings) to the same uniformly key distributed key.  Traditionally, their security is defined information-theoretically.  Fuzzy extractors have upper bounds on the length of the derived key~(Dodis et al., J. of Comp 2008).  In particular, the starting entropy of the source must be significantly higher than the logarithm of number of error patterns corrected.  For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as open problem.

Fuller, Meng, and Reyzin (Asiacrypt 2013) hypothesize that these bounds can be overcome by only providing security against computationally-bounded adversaries.  %They provide a construction of a computational fuzzy extractor that corrects a small number of errors without any loss in key length.  
%They show the feasibility of constructing a computational fuzzy extractor that does not suffer from the information-theoretic bounds.
%Unfortunately, their construction is limited to very high entropy distributions and does not significantly beat information-theoretic bounds.    In addition, we significantly improve on the allowable error rate and the required entropy rate of each block.  In particular we construct the following:
In this work, we provide the first construction of a fuzzy extractor for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.

\textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.  %Let $W = W_1, ..., W_\ell$ be a source distribution composed of blocks over a large alphabet, $Z$. To obfuscate a sample $w$ drawn from $W$.  We flip a coin $c_i$ for each block and either obfuscate the block $w_i$ or a random point in $Z$.  When a close reading $w'$ is given as input, we can recover most of the coins $c_i$.  Error-tolerance is achieved by sampling $c = c_1,..., c_\ell$ from an error-correcting code.  
Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).  
%Security holds as long as a large number of blocks $W_i$ of $W$  are unpredictable given equality queries on individual blocks.  
Our construction provides the following novel features:
\begin{itemize}
\item The source entropy is smaller than the log of the number of correctable error patterns.  
\item Constant error tolerance rate.  %Previous constructions of computational fuzzy extractors corrected a logarithmic fraction of errors.  (Information-theoretic constructions support a constant fraction of errors but are subject to bounds described above.)
\item Security for a large and meaningful class of distributions.  %The main requirement for security is that most blocks have a super-logarithmic amount of entropy.  Previous computational fuzzy extractors required the source to be essentially uniform. 
\end{itemize}
\end{abstract}

\section{Introduction}\label{sec:introduction}
Reliable key derivation is a cornerstone of authentication.  However, many sources with sufficient entropy for key derivation are noisy and provide similar but not identical values when the source is read multiple times~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}).  To use noisy physical sources in applications, two problems must be addressed.  The first is ensuring the same value is obtained from every reading of the source.  This must be done in a way that does not eliminate all the entropy from the output~(known as information-reconciliation~\cite{bennett1988privacy}).  The second is converting a source with entropy to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).  Both of these problems have interactive and non-interactive versions.  For a single user~(trying to produce the same key from multiple readings of a physical source) non-interactive solutions are appropriate.  We focus on this setting.  %If both of these tasks are achieved a noisy physical source can be used like a uniformly random private key.

@@

We consider the Hamming metric.  For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.  As we discuss later, it is possible to avoid these losses if the fuzzy extractor has additional knowledge about the distribution.} and logarithm of the number of error patterns to be corrected. For the remainder of this paper we denote this quantity by $gap$.  This represents a real problem as important biometrics~(such as irises~\cite{daugman2004}) have $gap <0$ and current fuzzy extractors provide no security guarantee.

@@

However, this does not need to be the case in the computational setting.  Fuller, Meng, and Reyzin define computational fuzzy extractors~\cite{fuller2013computational}.  Computational fuzzy extractors produce pseudorandom instead of truly random keys.  They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.  We resolve this question and construct a computational fuzzy extractor when $gap<0$.  This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.  A necessary condition for security is that a negligible portion of the probability distribution lies within any Hamming ball of radius $t$.  We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).

The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.  
In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.  Our focus is expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.

\textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.  Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or instead of recovering $w$ produce a new consistent high-entropy secret.  This is known as a fuzzy conductor~(the entropy is being ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.  Here, we follow the second approach and use a \emph{computational} fuzzy conductor.

@@

Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).  We would like to tolerate errors in $t$ individual blocks.  For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.  For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.  Thus, most bits of $c_i$ are recoverable. To tolerate errors we choose the coins $c$ from an error-correcting code.  Then, $c$ forms an distribution of high entropy.  This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.  It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.  Note, it is hard to recover $w$ from the value $c$.   This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.  
Our construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

Our construction provides several advantages over previous constructions of computational fuzzy extractors:
\begin{itemize}
\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss is necessary in a fuzzy extractor.  If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.  This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.   For an arbitrary distribution, this is at least the logarithm of the total number of error patterns.  The distributions supported by our construction are not error-correcting codes, we only require they are unpredictable in many dimensions~(see \defref{def:block guessable}).}
\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.  Our construction simply requires a large number of blocks that are unguessable given equality queries.  This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
\end{itemize}

@@

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.  For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.  The set of $\mathcal{I}^c$ is the set of all indices not contained in $\mathcal{I}$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   Let $|W|$ be the size of the support of $W$ that is $|W| = \{w | \Pr[W=w]>0\}$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.  For the Hamming metric, $|B_t| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  Unless otherwise noted logarithms are base $2$.
%\bnote{this is weird here and doesn't fit}  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).

@@

\subsection{Coding Theory}
\label{sec:coding theory}
We introduce some notions from the field of binary error correcting codes.  Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel~\cite{tallini2002capacity} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.  
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
\end{definition}
\textbf{Notes:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
The class of errors we support~($t$ Hamming errors over a large alphabet) in our source and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different~(see \consref{cons:first construction} for details).

@@

\begin{claim} 
\label{cl:many locations ent}
Let $C$ be a binary code and let $\mathcal{I}$ be a set of indices of $C$.  Then $\Hav(C | C_\mathcal{I}) = |C| - |\mathcal{I}|$.
\end{claim}
This claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}

@@

%\bnote{I don't think we need this!}
%\begin{definition}
%A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
%\end{definition}
%All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).  This is true as long as $C$ contains no constant bits.  Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.  For the remainder of this work when we say a code, we assume there are no constant bits.
%
%\begin{lemma}
%\label{lem:linear codes independent}
%Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
%\end{lemma}
%Proof in \apref{sec:proof of linear indep}.
%
%

@@

\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  
\label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
\begin{enumerate}
\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
\[
\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
\]
where the probability is taken over the randomness $r$.  \emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability over the random coin tosses $r$.  Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$, 
and for all binary predicates $\pi$, 
\[
|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
\]
where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.  Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
\end{enumerate}
\end{definition}

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.  With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary.

@@

In \apref{sec:conductors}, we show that fuzzy conductors are subject to the same lower bounds on entropy loss as fuzzy extractors.  Instead of using a fuzzy conductor, we define a computational version.  
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has 
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
\end{definition}

@@

Before describing our construction, we recall the problem we are trying address.  The goal is to derive strong keys from noisy sources.  As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is small or even negative.
In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.  Thus, we focus on providing enough security when $gap<0$.  We build a computational fuzzy conductor, noting that it can be converted to a computational fuzzy extractor using \lemref{lem:cond and cext}.%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).  Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.  As described in Fuller, Meng, and Reyzin~\cite{fuller2013computational}, use of a computational fuzzy extractor may allow a construction when $gap = O(\log n)$.  Their construction is only applicable for high entropy input and yield a result when $gap$ is small.  We will provide the first construction where $gap$ is negative.

>>>>

\begin{abstract} 
Fuzzy extractors derive strong keys from noisy sources.  The goal is to reliably convert a high entropy source~(which may have different values on repeated readings) to the same uniformly distributed key.  Traditionally, their security is defined information-theoretically.  Fuzzy extractors have upper bounds on the length of the derived key~(Dodis et al., J. of Comp 2008).  In particular, the starting entropy of the source must be significantly higher than the logarithm of number of error patterns corrected.  For many practical noisy sources, like biometrics, this condition is not fulfilled, leaving reliable key derivation from these sources as open problem.

Fuller, Meng, and Reyzin (Asiacrypt 2013) hypothesize that these bounds can be overcome by only providing security against computationally-bounded adversaries. 
In this work, we provide the first construction of a fuzzy extractor for a large class of distributions where the starting entropy is smaller than the logarithm of the number of correctable error patterns.

\textbf{Construction:} We construct a computational fuzzy extractor based on obfuscation of point functions.  
Our construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).  
Our construction provides the following novel features:
\begin{itemize}
\item The source entropy is smaller than the log of the number of correctable error patterns.  
\item Constant error tolerance rate.  
\item Security for a large and meaningful class of distributions.  \bnote{this description needs to be better}.
\end{itemize}
\end{abstract}

\section{Introduction}\label{sec:introduction}
Reliable key derivation is a cornerstone of authentication.  However, many sources with sufficient entropy for key derivation are noisy and provide similar but not identical values when the source is read multiple times~(examples include biometrics~\cite{daugman2004} and physically unclonable functions~\cite{pappu2002physical}). \bnote{add more examples here} To use noisy physical sources in applications, two problems must be addressed.  The first is ensuring the same value is obtained from every reading of the source.  This must be done in a way that does not eliminate all the entropy from the output~(known as information-reconciliation~\cite{bennett1988privacy}).  The second is converting the entropic source to a uniform random key~(privacy amplification~\cite{bennett1988privacy}).  Both of these problems have interactive and non-interactive versions.  For a single user~(trying to produce the same key from multiple readings of a physical source) the non-interactive solutions are appropriate.  We focus on this setting.  %If both of these tasks are achieved a noisy physical source can be used like a uniformly random private key.

@@

We consider the Hamming metric.  For the Hamming metric, the key may be no longer than the difference between the starting entropy of the source\footnote{We assume that the fuzzy extractor operates independently of the source $W$.  As we discuss later, it is possible to avoid these losses if the fuzzy extractor has additional knowledge about the distribution.} and logarithm of the number of error patterns to be corrected. For the remainder of this paper we denote this quantity by $gap$.  This represents a real problem, important biometrics, such as irises~\cite{daugman2004}, have $gap <0$ and current fuzzy extractors provide no security guarantee.

@@

This does not need to be the case in the computational setting.  Fuller, Meng, and Reyzin define computational fuzzy extractors~\cite{fuller2013computational}.  Computational fuzzy extractors produce pseudorandom instead of truly random keys.  They hypothesize a computational fuzzy extractor may exist with a small or negative $gap$.  We resolve this question and construct a computational fuzzy extractor when $gap<0$.  This is impossible for an arbitrary min-entropy distribution as every point could be within distance $t$.  A necessary condition for security is that a negligible portion of the source's probability distribution lies within any Hamming ball of radius $t$.  We require a stronger condition that many blocks are unpredictable~(\defref{def:block guessable}).

The goal of an information-theoretic fuzzy extractor is to output a maximal length key for a source $W$.  
In the computational setting, a key may be expanded once it is long enough to serve as input to a pseudorandom generator.  Our focus is on expanding the class of distributions for which we can provide meaningful security, and remember keys can be expanded once they are long enough.

\textbf{Overview of Construction:}  Fuller, Meng, and Reyzin~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} show that replacing an information-theoretic information-reconciliation component with a computational component is unlikely to be fruitful.  Instead, the authors suggest two alternatives: combine the information-reconciliation and privacy amplification components~(their approach) or produce a new consistent high-entropy secret instead of recovering $w$.  This is known as a fuzzy conductor~(the entropy is ``conducted'' from $w$ to a new distribution) and was introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}.  Here, we follow the second approach and use a \emph{computational} fuzzy conductor.

@@

Consider a source $W = W_1,..., W_\ell$ that is split into blocks~(over a large alphabet).  We would like to tolerate errors in $t$ individual blocks.  For each block $i$, we flip a coin $c_i$ and either obfuscate $I_{w_i}$ or pick a random point $r_i$ and obfuscate $I_{r_i}$.  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rec$ then runs the obfuscated program $P_i$ on $w_i'$ and checks whether $P_i(w_i')=1$.  For most locations $i$, \rep can determine whether $w_i$ or a random value was the point obfuscated.  Thus, most bits of $c_i$ are recoverable. To tolerate errors we choose the coins $c$ from an error-correcting code.  The set of possible codewords forms a high entropy distribution.  This construction conducts entropy from $w$ to $c$ and is a computational fuzzy conductor.  It may be converted to a computational fuzzy extractor by either information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors.  Note, it is hard to recover $w$ from the value $c$.   This is necessary to overcome the information-theoretic lower bounds~\cite[Section 3.3]{fuller2013computational}.  
Our construction is inspired by Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.

Our construction provides several advantages over previous constructions of computational fuzzy extractors:
\begin{itemize}
\item The first computational fuzzy extractor where $gap$ may be negative for a large class of distributions.\footnote{There are examples where no loss is necessary in a fuzzy extractor.  If $W$ consists of points from an error-correcting code of sufficient minimum distance, then no public information is necessary and $gap$ may be negative.  This is not in the spirit of a fuzzy extractor as the distribution is already ``error-corrected.''  For arbitrary min-entropy sources, analysis of information-theoretic fuzzy extractors proceeds by arguing an adversary learns at most a bit for each bit necessary for error correction.   For an arbitrary distribution, this is at least the logarithm of the total number of error patterns.  The distributions supported by our construction are not error-correcting codes, we require unpredictability in many dimensions~(see \defref{def:block guessable}).}
\item The first computational fuzzy extractor that allows for a constant fraction of errors.  Previous constructions could correct only  a logarithmic fraction of errors~($O(\frac{\log \ell}{\ell})$)
\item The first computational fuzzy extractor where blocks are not required to be uniformly distributed.  Our construction simply requires a large number of blocks that are unguessable given equality queries.  This subsumes the distributions supported by~\cite[Construction 4.1]{fuller2013computational}.
\end{itemize}

@@

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.  For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.  The set $\mathcal{I}^c$ is the complement of $\mathcal{I}$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   Let $|W|$ be the size of the support of $W$ that is $|W| = |\{w | \Pr[W=w]>0\}|$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. 
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.  For the Hamming metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  Unless otherwise noted logarithms are base $2$.
%\bnote{this is weird here and doesn't fit}  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).

@@

\subsection{Coding Theory}
\label{sec:coding theory}
We introduce some notions from the field of binary error correcting codes.  Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel~\cite{tallini2002capacity} where there are flips from $0\rightarrow 1$ but no bit flips from $1\rightarrow 0$.  
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
\end{definition}
\textbf{Notes:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
The class of errors we support~($t$ Hamming errors over a large alphabet) in our source and the class of errors corrected by our code~($t$ $0\rightarrow 1$ errors) are different~(see \consref{cons:first construction} for details).  Codes where $\log |C| = \Theta(\ell)$ and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.

@@

\begin{claim} 
\label{cl:many locations ent}
Let $C$ be a binary code and let $\mathcal{I}^c$ be a set of indices of $C$.  Then $\Hav(C | C_{\mathcal{I}^c}) = \log |C| - |\mathcal{I}^c|$.
\end{claim}
This claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}

@@

%\bnote{I don't think we need this!}
%\begin{definition}
%A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
%\end{definition}
%All binary linear codes~(without constant bits) are output equiprobable and .  This is true as long as $C$ contains no constant bits.  Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.  For the remainder of this work when we say a code, we assume there are no constant bits.
%
%\begin{lemma}
%\label{lem:linear codes independent}
%Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
%\end{lemma}
%Proof in \apref{sec:proof of linear indep}.
%
%

@@

\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  
\label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
\begin{enumerate}
\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
\[
\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
\]
where the probability is taken over the randomness $r$.  \emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability over the random coin tosses $r$.  Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$, 
and for all binary predicates $\pi$, 
\[
|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
\]
where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.  Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
\bnote{We never need to run our simulator so I think we can use virtual gray-box.}
\end{enumerate}
\end{definition}

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$ there is no guarantee about the probability of correctness.
The definition of computational fuzzy extractors specifies a family of sources for which the fuzzy extractor works rather than the family of all sources of a given min-entropy $m$.  With $gap<0$ there are distributions contained in a single Hamming ball, so restricting the family of sources is necessary.

@@

In \apref{sec:conductors}, we show that fuzzy conductors are subject to the same lower bounds on entropy loss as fuzzy extractors.  To overcome these bounds, we use a computational version of a fuzzy conductor.  
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has 
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
\end{definition}

@@

Before describing our construction, we recall the problem we are trying address.  The goal is to derive strong keys from noisy sources.  As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is small or even negative.
In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.  Thus, we focus on providing enough security when $gap<0$.  We build a computational fuzzy conductor, which can be converted to a computational fuzzy extractor using a computational extractor~(\lemref{lem:cond and cext}).%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).  Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.  As described in Fuller, Meng, and Reyzin~\cite{fuller2013computational}, use of a computational fuzzy extractor may allow a construction when $gap = O(\log n)$.  Their construction is only applicable for high entropy input and yield a result when $gap$ is small.  We will provide the first construction where $gap$ is negative.
